---
title: "Substitutions"
output: html_notebook
---

 
# /scratch/wally/FAC/FBM/DBC/amalaspi/virome/yarizmen/simulations_Feb_2020b/Prueba/Sustituciones/Total_Match_Mismatch_CIGAR_VDiarr_* The first column is the number of matches, the second column the number of mismatches. There’s one row per read. The last part of the file name gives you the qShift value used, e.g. for Total_Match_Mismatch_CIGAR_VDiarr_neg_10 a qShift value of -10 was used.
```{r}
library(data.table)
path <- "/Users/sneuensc/Sapfo/virome_yami/seq_error_substitution/"

lengths <- c(0, 1, 3, 5, 7, 9, 11, 13, 15)
lengths <- c(0, 3, 7, 11)

data1 <- NULL
for(i in lengths){
  tmp <- fread(paste0(path, "Total_Match_Mismatch_CIGAR_VDiarr_neg_", i))
  #tmp2 <- data.frame(table(tmp$V2))
  data1 <- rbind(data1, c(sum(tmp$V2) / nrow(tmp), i))
}
colnames(data1) <- c("sub","length")
data1 <- data.table(data1)
data1$model <- "sequencing_error"
data1$length <- -1 * data1$length
to.error <- function(x)return(round(1/(10^(x/10)),1))
data1$length2 <- to.error(data1$length)

data1$text <- paste0(to.error(data1$length) , " (", data1$length, ")")
data1$text <- factor(data1$text, levels = data1$text)


```

```{r}
#/scratch/wally/FAC/FBM/DBC/amalaspi/virome/yarizmen/simulations_Feb_2020b/results_Mapeo_No_Deam_length_60 without deamination
#/scratch/wally/FAC/FBM/DBC/amalaspi/virome/yarizmen/simulations_Feb_2020b/Deamination/Deam_singlstr_0/results_Mapeo with 0.05 deamination
#/scratch/wally/FAC/FBM/DBC/amalaspi/virome/yarizmen/simulations_Feb_2020b/Deamination/Deam_singlstr_3/results_Mapeo_Deam_3 with 0.3 deamination
#/scratch/wally/FAC/FBM/DBC/amalaspi/virome/yarizmen/simulations_Feb_2020b/Deamination/Deam_singlstr_5/results_Mapeo_Deam_5 with 0.5 deamination

library(data.table)
library(ggplot2)
path <- "/Users/sneuensc/Sapfo/virome_yami/deamination_substitution/"
files <- list.files(path)

f <- files[1]

lengths <- c('no','0','3','5' )
lengths <- c('0','3','5' )

data2 <- NULL
for(i in lengths){
  tmp <- fread(paste0(path, "misincorporation_", i, ".txt"))
  data2 <- rbind(data2, c(sum(tmp[1:60, 10:21]) / tmp$Total[1], i))
}
colnames(data2) <- c("sub","length")
data2 <- data.table(data2)
data2$model <- "deamination"
data2$length[-1] <- as.numeric(paste0("0.", data2$length[-1]))
data2$sub <- as.numeric(data2$sub)
data2$length <- factor(data2$length, levels = data2$length)
```


```{r}

ymax <- max(data1$sub, data2$sub)
b <- ggplot(data1, aes(x = text, y = sub)) +
  geom_bar(stat="identity") +
  geom_text(aes(label = round(sub,2)), position=position_dodge(width=0.9), vjust=-0.25, cex=3.5) +
  xlab("fold increase of substitutions (qShift)") +
  ylab("Mean number of substitutions [per 60bp]") +
  ylim(0,ymax) +
  theme_classic() +
  ggtitle("B. Sequencing error simulations") +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major.y = element_line())

a <- ggplot(data2, aes(x = length, y = sub)) +
  geom_bar(stat="identity") +
  geom_text(aes(label = round(sub,2)), position=position_dodge(width=0.9), vjust=-0.25, cex=3.5) +
  xlab("single-stranded probability of deamination") +
  ylab("Mean number of substitutions [per 60bp]") +
  ylim(0,ymax) +
  theme_classic() +
  theme(panel.grid.major.y = element_line()) +
  ggtitle("A. Deamination simulations")

file <- "/Users/sneuensc/Dropbox (popgen)/Virome/PLoS_ONE_virome/sam/figure_3_substitutions.pdf"
  library(gridExtra)
  library(grid)
  
  lay <- rbind(c(rep(1,5), rep(2, 6)))
  grob <- grid.arrange(grobs=list(a, b), layout_matrix=lay)   
  
  ggsave(file, width = 297, height = 210, scale=0.8, units = "mm", grob)
```

